When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-29 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
updated number of participants
made M plusminus SD

Data was collected between the 16th of August 2022 and the 3rd of February 2023.
All of the $N=`r n_quest`$ participants who filled out the online questionnaires came to the first lab session.
Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the $n$-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
Our final data set therefore included $N=`r nrow(data_quest)`$ participants (`r round((table(data_quest$gender)[2]/nrow(data_quest))*100, digits = 1)`% female, $M=`r round(mean(data_quest[,"age"]), digits = 1)`$ ($SD=`r round(sd(data_quest[,"age"]), digits = 1)`$)\ years old), which is `r format(round(nrow(data_quest)/53, digits = 1), nsmall = 1)` times more than what the highest sample size calculation required.

>>>>

Data was collected between the 16th of August 2022 and the 3rd of February 2023.
Of the $N=`r n_quest`$ participants who filled out the online questionnaires, $n=`r nrow(data_quest)`$ came to the first lab session.
Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the $n$-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
Our final data set therefore included $N=`r nrow(data_quest)`$ participants (`r round((table(data_quest$gender)[2]/nrow(data_quest))*100, digits = 1)`% female, $M±SD=`r format(round(mean(data_quest[,"age"]), digits = 1), nsmall = 1)`±`r round(sd(data_quest[,"age"]), digits = 1)`$)\ years old), which is `r format(round(nrow(data_quest)/53, digits = 1), nsmall = 1)` times more than what the highest sample size calculation required.
